SI

### 2021-05-07 ms/data_readme.Rmd
Change date of data readme creation
Update data README Rmd

Title of Dataset: Data from: Intergenerational niche differentiation in filmy
ferns (Hymenophyllaceae)

@@

Department of Integrated Biosciences, Graduate School of Frontier Sciences,
The University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa, Chiba 277-8562, Japan
joelnitta@gmail.com

@@

Recommended citation for the data: Nitta JH, Watkins JE, Holbrook NM, Wang TW,
Davis CC (2021) Data from: Intergenerational niche differentiation in filmy
ferns (Hymenophyllaceae) https://doi.org/10.6084/m9.figshare.14184572

Citation for and links to publications that cite or use the data: Nitta JH,
Watkins JE, Holbrook NM, Wang TW, Davis CC (2021) Intergenerational niche
differentiation in filmy ferns (Hymenophyllaceae) <<FIXME: ADD JOURNAL>>

@@

@@

@@

@@

@@

@@

@@

- date_time: Date and time, formatted YYYY-MM-DD HH-MM-SS.
- temp: Temperature (degrees Celsius)
- rh: Relative humidity (%)
- salt: Name of salt used to maintain constant humidity in the desiccation
chamber (see methods above for corresponding relative humidity).
- generation: Gametophyte or sporophyte, or "mixed" if samples of both generations
were present in the growth chamber.
- year: Year.
- species: Species.
- file: Name of file containing raw data.
- serial_no: Serial number of datalogger.

@@

@@

@@

@@

@@

2021-03-14

>>>>

Title of Dataset: Data from: Ecophysiological differentiation between life stages in filmy ferns (Hymenophyllaceae)

@@

Department of Biological Sciences, Graduate School of Science, The University 
of Tokyo, 2-11-16 Yayoi, Bunkyo-ku, Tokyo 113-0032, Japan 
joelnitta@gmail.com

@@

Recommended citation for the data: Nitta JH, Watkins JE, Holbrook NM, Wang TW,
Davis CC (2021) Data from: Ecophysiological differentiation between life stages 
in filmy ferns (Hymenophyllaceae) https://doi.org/10.6084/m9.figshare.14184572

Citation for and links to publications that cite or use the data: Nitta JH,
Watkins JE, Holbrook NM, Wang TW, Davis CC (2021) Ecophysiological differentiation 
between life stages in filmy ferns (Hymenophyllaceae) (Hymenophyllaceae) <<FIXME: ADD JOURNAL>>

@@

Checksums are 32-byte MD5 hashes generated with tools::md5sum() in R.

@@

MD5 checksum: `r tools::md5sum(here::here(gameto_times_2012_file))`

@@

MD5 checksum: `r tools::md5sum(here::here(sporo_dt_times_file))`

@@

MD5 checksum: `r tools::md5sum(here::here("data/data_raw.tar.gz"))`

@@

MD5 checksum: `r tools::md5sum(here::here(specimens_raw_file))`

@@

MD5 checksum: `r tools::md5sum(here::here(filmy_dt_file))`

@@

- date_time: Date and time, formatted YYYY-MM-DD HH-MM-SS.
- temp: Temperature (degrees Celsius)
- rh: Relative humidity (%)
- salt: Name of salt used to maintain constant humidity in the desiccation
chamber (see methods above for corresponding relative humidity).
- generation: Gametophyte or sporophyte, or "mixed" if samples of both life stages
were present in the growth chamber.
- year: Year.
- species: Species.
- file: Name of file containing raw data.
- serial_no: Serial number of datalogger.

@@

MD5 checksum: `r tools::md5sum(here::here(filmy_dt_chamber_file))`

@@

MD5 checksum: `r tools::md5sum(here::here(filmy_habit_file))`

@@

MD5 checksum: `r tools::md5sum(here::here(light_data_file))`

@@

2021-05-07

- Update specimens.csv in raw data.

@@

2021-05-06

- Add MD5 checksums.
- Correct missing values in 'date_collected' column of fern_specimens.csv from 'NA-NA-NA'
to 'NA'.
- Change title of paper.
- Change address of first author.
- Change description of "generation" to "life stage".

2021-03-13
